Multiple Kernelized Correlation Filters based High Speed Target Following

### 2017-04-05 draft.tex
MKCF Part Added

\section{Multiple Kernelized Correlation Filter Based Tracking}
\label{sc:MKCF}

>>>>

\section{Multiple Kernelized Correlation Filter Based Tracking}
\label{sc:MKCF}
The KCF with Multi-channel features outperforms the other state-of-the-art object traking algorithms both in terms of run-time performance and tracking accuracy. However, it lack scale adaptation module or the naive scale adaptation method added into the KCF reduces the frames per second from $\geq300$ fps to less than $100$ fps. One straightforward method is to run detection on ROIs with different sizes determined by pre-defined scale ratios \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All these method increases the computational complexity of tracking by running detection on a number of ROIs. Another scale update method in Correlation Filter framework was proposed by \cite{zhang2014fast}. It uses the MOSSE tracker to estimate translation of an object. The scale is updated in a naive way where the confidence map is used to determine the scale change between successive frames. For instance, their method assumes similar scale in between two consecutive frames given similar confidences. With this simple method, we do not need to run detection on different ROIs at a given frame and perform tracking at $\geq300$ fps. In this study, we propose the use of Multiple KCFs in an intuitive way to perform robust scale-adaptive tracking at more than $300$ fps. Our approach is inspired by \cite{ma2015long} where two KCFs are employed as translation and scale filters. It first estimates translation using the translation filter learned on \textit{target}$+$\textit{background} area. Then, the scale filter learned on the \textit{target} area is used to estimate new scale of the target at the estimated position. Application of translation and scale filter at each frame reduces run-time performance ($\leq50 fps$) as we need to run detection and training on both filters. Similarly, we learn three different correlation filters specializing on different aspects of tracking and addresses the weakness of each other, resulting in more robust tracking. We name these filters as \textit{target}+\textit{small background} translation filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and \textit{target}+\textit{large background} translation filter ($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at each frame, we can achieve the targeted operation frame rate.
\begin{figure}[!t]
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters called as medium ROI translation filter, target ROI scale filter and large ROI translation filter are shown. Also, the hanning window and desired Gaussian response for each filter are displayed.}
\label{fig:Filters}
\end{figure}
